On the propriety of restricted Boltzmann machines

### 2016-12-01 writing/draft.Rmd
forgot one more edit

It should be noted that BwTNLV (2.) and BwTNML (3.) are drawing from the same stationary posterior distribution for vectors of visibles. The difference between these two methods is in how well the chains mix and how quickly they arrive at the target posterior distribution. After a burn-in period of 50 iterations selected by inspecting the trace plots, we assess the issue of mixing in two ways. First, the autocorrelation functions (ACF) from each posterior sample corresponding to a model probability for a visible vector outcome $\mathbf{v}=(v_1,v_2,v_3,v_4)\in\{\pm 1\}^4$ (i.e., computed from $\boldsymbol \theta$ under (\ref{eqn:pmf})) of visibles are assessed and plotted in Figure \ref{fig:acf} with BwTNLV in black and BwTNML in red. As expected, ACF corresponding to the method that marginalizes out the hidden variables from the likelihood decreases to zero at a much faster rate, indicating better mixing for the chain.

>>>>

It should be noted that BwTNLV (2.) and BwTNML (3.) are drawing from the same stationary posterior distribution for vectors of visibles. The difference between these two methods is in how well the chains mix and how quickly they arrive at the target posterior distribution. After a burn-in period of 50 iterations selected by inspecting the trace plots, we assess the issue of mixing in two ways. First, the autocorrelation functions (ACF) from each posterior sample corresponding to a model probability for a visible vector outcome $\mathbf{v}=(v_1,v_2,v_3,v_4)\in\{\pm 1\}^4$ (i.e., computed from $\boldsymbol \theta$ under (\ref{eqn:pmf})) are assessed and plotted in Figure \ref{fig:acf} with BwTNLV in black and BwTNML in red. As expected, ACF corresponding to the method that marginalizes out the hidden variables from the likelihood decreases to zero at a much faster rate, indicating better mixing for the chain.
